Water Management

### 2020-02-11 Paper/paper.tex
rename subsection
remove blindtext
section regarding the effect of discount factors

\subsection{Implementation} % TODO: Better title?

@@

Finally, we want to compute the value of the steady state by using a monte carlo simulation.

	\subsection{bla}
	\begin{figure}[ht] % TODO remove example
		\includegraphics[width=1\textwidth]{figures/example.png}
		\caption{Example Image}
		\label{fig:example-pic}
	\end{figure}
	\blindtext
	\begin{figure}[ht] % TODO remove example
		\begin{longtable}{|p{2,5cm}|p{2,5cm}|p{2,5cm}|p{3cm}|p{3cm}|}
			\hline
			&\multicolumn{4}{c|}{\textbf{Klasse}} \\
			\hline
			& \textbf{S0} & \textbf{S1} & \textbf{S2} & \textbf{S3} \\
			\hline
			\textbf{lorem} & ipsum & ipsum & ipsum & ipsum \\
			\hline
		\end{longtable}
		\label{fig:example-figure}
		\caption{Example Table}
	\end{figure}
	\blindtext
	\blindtext
	\blindtext

@@

	The result is put in a histogram and shown in figure \ref{fig:steadyStateMonteCarlo}
		\includegraphics[width=1\textwidth]{figures/steadyStateMonteCarlo.eps}
		\caption{Steady State Probability}
		\label{fig:steadyStateMonteCarlo}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	\subsection{Changed Volatility of Rainfalls}

>>>>

\subsection{Computation of the value function}

@@

% Finally, we want to compute the value of the steady state by using a monte carlo simulation. 
% TODO: hier steady state und monte carlo simulation erklären oder besser in results?

@@

	The result is put in a histogram and shown in figure \ref{fig:steadyStateMonteCarlo}.
	The highest possibility for a steady state is around 4.2. 
	In edge cases one can find steady states as low as 3.5 or as high as 5.2. 
	The curve resembles a normal distribution.

	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/steadyStateMonteCarlo.eps}
		\caption{Steady State Probability}
		\label{fig:steadyStateMonteCarlo}
	\end{figure}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	When altering the discount factor $\beta$ in a range from 0 to 1, the optimal irrigation policy changes.
	Looking at small water levels within the reservoir the optimal irrigation amount does not change much depending on the discount factor.
	A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. 
	This leads to a increasing gap between irrigation amounts over $\beta$ with increasing water level since conserving water does not increase the usage as much.
	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/optimum-policy-over-beta.eps}
		\caption{Optimal irrigation policy as a function of the discount factor $\beta$}
		\label{fig:optimal-irrigation-beta}
	\end{figure}
	\subsection{Changed Volatility of Rainfalls}
